### 2019-04-16 Writing/Tables/Full_Tab_pooledsmethods_test.tex
added the looooong tables
Updated analysis
Updated results

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 13:20:38 2018
\begin{table}[ht]
\centering
\begin{tabular}{lllrrr}
  \hline
comp & metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
Best & RF & bayesian:parsimony & 0.891 & 579437.500 & 0.000 \\ 
   &  & bayesian:parsimony & 0.984 & 470621.500 & 0.168 \\ 
   & Tr & bayesian:parsimony & 0.847 & 657875.500 & 0.000 \\ 
   &  & bayesian:parsimony & 0.975 & 499754.000 & 0.000 \\ 
  Null & RF & bayesian:parsimony & 0.891 & 579437.500 & 0.000 \\ 
   &  & bayesian:parsimony & 0.984 & 470621.500 & 0.168 \\ 
   & Tr & bayesian:parsimony & 0.847 & 657875.500 & 0.000 \\ 
   &  & bayesian:parsimony & 0.975 & 499754.000 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)} 
\label{Full_Tab_pooledsmethods_test}
\end{table}

>>>>

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 16:10:50 2019
\begin{table}[ht]
\centering
\begin{tabular}{lllrrr}
  \hline
comp & metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
Best & RF & bayesian:parsimony & 0.939 & 192659.000 & 0.000 \\ 
   &  & bayesian:parsimony & 0.986 & 157677.500 & 0.082 \\ 
   & Tr & bayesian:parsimony & 0.944 & 193142.000 & 0.000 \\ 
   &  & bayesian:parsimony & 0.975 & 161621.000 & 0.008 \\ 
  Null & RF & bayesian:parsimony & 0.939 & 192659.000 & 0.000 \\ 
   &  & bayesian:parsimony & 0.986 & 157677.500 & 0.082 \\ 
   & Tr & bayesian:parsimony & 0.944 & 193142.000 & 0.000 \\ 
   &  & bayesian:parsimony & 0.975 & 161621.000 & 0.008 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)} 
\label{Full_Tab_pooledsmethods_test}
\end{table}

### 2019-04-16 Writing/Tables/Tab_pooledmethod.tex
Updated results

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:14 2018
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
metric & method & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
RF & bayesian & 0.319 & 0.714 & 0.828 & 0.811 & 0.934 & 1.000 \\ 
   & parsimony & 0.076 & 0.496 & 0.679 & 0.684 & 0.911 & 1.000 \\ 
  Tr & bayesian & -0.473 & 0.354 & 0.738 & 0.618 & 0.947 & 1.000 \\ 
   & parsimony & -0.436 & 0.258 & 0.601 & 0.568 & 0.949 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Summary statistics of the normalised distances to the best or null tree for the pooled methods.} 
\label{Tab_pooledmethod}
\end{table}

>>>>

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 16:08:54 2019
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
metric & method & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
RF & bayesian & 0.385 & 0.753 & 0.851 & 0.824 & 0.924 & 1.000 \\ 
   & parsimony & 0.371 & 0.642 & 0.739 & 0.742 & 0.865 & 1.000 \\ 
  Tr & bayesian & -0.196 & 0.560 & 0.802 & 0.717 & 0.945 & 1.000 \\ 
   & parsimony & -0.155 & 0.525 & 0.750 & 0.693 & 0.900 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Summary statistics of the normalised distances to the best or null tree for the pooled methods.} 
\label{Tab_pooledmethod}
\end{table}

### 2019-04-16 Writing/Tables/Tab_pooledscenarios_test.tex
Updated results

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.573 & 356436.000 & \textbf{0} \\ 
   & maxi:rand & 0.873 & 287225.000 & \textbf{0} \\ 
   & mini:rand & 0.856 & 95841.500 & \textbf{0} \\ 
  Tr & maxi:mini & 0.614 & 358800.000 & \textbf{0} \\ 
   & maxi:rand & 0.908 & 288223.500 & \textbf{0} \\ 
   & mini:rand & 0.858 & 98507.500 & \textbf{0} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction)} 
\label{Tab_pooledscenarios_test}
\end{table}

>>>>

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 16:07:23 2019
\begin{table}[ht]
\centering
\begin{tabular}{llr|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.848 & 32012.500 & 0.000 \\ 
   & maxi:rand & 0.941 & 44161.000 & 0.000 \\ 
   & mini:rand & 0.954 & 80382.500 & 0.000 \\ 
  Tr & maxi:mini & 0.992 & 60680.500 & 0.839 \\ 
   & maxi:rand & 0.980 & 60447.000 & 0.713 \\ 
   & mini:rand & 0.982 & 64222.500 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correction)} 
\label{Tab_pooledscenarios_test}
\end{table}
